Neural Circuit Discovery

### 2013-11-14 docs/paper/paper.tex
well i guess it's time to make the plotting not suck
added a bunch of figures

@@

\subsubsection{Mouse Retina}
intro paragraph about retina data

@@

@@

>>>>

\begin{figure}
  \centering 
  \caption{This is the pedagogy figure where we explain what is is that the model does }
\end{figure}

@@

\begin{figure}
  \centering 
  \caption{This is the synthetic data figure where we show that our model works with synthetic data across a variety of topologies and geometries}
\end{figure}

\subsubsection{Mouse Retina}

\begin{figure}
  \centering 
  \caption{Mouse retina data}
\end{figure}

\autocite{retina} used serial-section electron microscopy to acquire the connectome
of a 100um x 70 um region of the mouse retina, measuring the number of putative
synaptic touch-points between nearly 1000 cells.

@@

\begin{figure}
  \centering 
  \caption{C elegans data}
\end{figure}

@@

\begin{figure}
  \centering 
  \caption{Microprocessor data}
\end{figure}
